---
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: 
  bookdown::pdf_document2:
    toc: no
geometry: margin = 1in
fontsize: 11pt
bibliography: thesis-references.bib
csl: science-modified1.csl
link-citations: yes
linkcolor: blue
urlcolor: blue
header-includes:
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \usepackage{microtype}
- \counterwithin{figure}{section}
- \counterwithin{table}{section}
- \setlength{\parindent}{1em}
- \doublespacing
- \usepackage{float}
- \usepackage{amsmath}
- \DeclareMathOperator{\logit}{logit}
---

<!--R version 3.4.1 (2017-06-30)-->

```{r knitr.global_options, include=F}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
```

```{r load.packages, include=F}

# Load pacman, installing as necessary.
my_repo <- 'http://cran.r-project.org'
if (!require("pacman")) {install.packages("pacman", repos = my_repo)}

# Load the other packages, installing as needed.
pacman::p_load(knitr, bookdown, reshape2, tidyverse, lubridate, ggthemes, png, 
               grid, gridExtra, beeswarm)

## Source: https://github.com/koundy/ggplot_theme_Publication/blob/master/R/ggplot_theme_Publication.R

theme_HEI <- function(base_size=14) {
  library(grid)
  library(ggthemes)
  (theme_foundation(base_size=base_size)
  + theme(plot.title = element_text(face = "bold",
                                    size = rel(1.2), hjust = 0.5),
          text = element_text(),
          panel.background = element_rect(colour = NA),
          plot.background = element_rect(colour = NA),
          panel.border = element_rect(colour = NA),
          axis.title = element_text(face = "bold",size = rel(1)),
          axis.title.y = element_text(angle=90,vjust =2),
          axis.title.x = element_text(vjust = -0.2),
          axis.text = element_text(), 
          axis.line = element_line(colour="black"),
          axis.ticks = element_line(),
          panel.grid.major = element_line(colour="#f0f0f0"),
          panel.grid.minor = element_blank(),
          legend.key = element_rect(colour = NA),
          legend.position = "bottom",
          legend.direction = "horizontal",
          legend.key.size= unit(0.6, "cm"),
          legend.margin = unit(0, "cm"),
          legend.title = element_blank(),
          plot.margin=unit(c(10,5,10,5),"mm"),
          strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
          strip.text = element_text(face="bold")
  ))
  
}

```

\pagenumbering{gobble}

```{r child = '01-titlepage.Rmd'}
```

\newpage

```{r child = '02-copyright.Rmd'}
```

\newpage

```{r child = '03-abstract.Rmd'}
```

\FloatBarrier

\newpage
\fancyhead[LE,RO]{}
\fancyhead[LO,RE]{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancy}
\pagenumbering{roman}
\fancyhead[CO,CE]{Table of Contents}
\setcounter{tocdepth}{3}
\linespread{1}\selectfont
\tableofcontents

\FloatBarrier

\newpage
\fancyhead[CO,CE]{List of Figures}
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\FloatBarrier

\newpage
\fancyhead[CO,CE]{List of Tables}
\addcontentsline{toc}{section}{List of Tables}
\listoftables

\FloatBarrier

\newpage
\fancyhead[CO,CE]{Acknowledgements}
\section*{Acknowledgements}

```{r child = '04-acknowledgements.Rmd'}
```

\FloatBarrier

\clearpage

\pagenumbering{arabic}
\fancyhead[CO,CE]{Chapter 1. Introduction}

```{r child = '05-chapter1.Rmd'}
```

\FloatBarrier

\clearpage

\fancyhead[CO,CE]{Chapter 2. Photo Journalism}

```{r child = '06-chapter2.Rmd'}
```

\FloatBarrier

\clearpage

\fancyhead[CO,CE]{Chapter 3. Webbing Fluid}

```{r child = '07-chapter3.Rmd'}
```

\FloatBarrier

\clearpage

\fancyhead[CO,CE]{Chapter 4. Fighting Crime}

```{r child = '08-chapter4.Rmd'}
```

\FloatBarrier

\clearpage

\fancyhead[CO,CE]{Chapter 5. Conclusions}

```{r child = '09-chapter5.Rmd'}
```

\FloatBarrier

\newpage
\fancyhead[CO,CE]{References}
\linespread{1.0}\selectfont

# References

\setlength{\parindent}{0cm} 

<div id="refs"></div>

\FloatBarrier

\newpage
\fancyhead[CO,CE]{Acronyms and Abbreviations}
\linespread{1.0}\selectfont

# Acronyms and abbreviations

```{r acronyms, message=F, warnings=F, results='asis', echo=F}
tabl <- " 
----------------------------------------------------------------------------------------
Code               Full name            
------------------ ---------------------------------------------------------------------
AM                 Arithmetic Mean

API                Application Programmable Interface

ASD                Arithmetic Standard Deviation

CDC                Centers for Disease Control and Prevention

WAC                Washington Administrative Code

WSU                Washington State University

Zn                 Zinc
----------------------------------------------------------------------------------------

"
cat(tabl)
```

\FloatBarrier

\newpage
\fancyhead[CO,CE]{Vita}
\linespread{1.0}\selectfont

```{r child = '10-vita.Rmd'}
```

